Global optimization method with dual Lipschitz constant estimates for problems with non-convex constraints

### 2020-01-21 2019/NUMTA_Barkalov/Special Issure/article.tex
Add illustrations and several tables

\section{Numerical experiments}

@@

\section{TEST}

\cite{Evtushenko1971, Piyavskii1972, Shubert1972, Strongin1970, Evtushenko2009, Evtushenko2013, Strongin2000, Sergeyev2013, Pinter1996, Jones2009, Wood1991, Meewella1988, Mladineo1986, Vaz2009, Stripinis2019, Paulavicius2016, Pillo2012, Pillo2016, Barkalov2017_1, Barkalov2017_2, Sergeyev2006, Zilinskas2008, Sovrasov2019, Kvasov2003, Sergeyev2010,Sergeyev2016, Horst1996, Gablonsky2001, Jones1993, Gaviano2003, Barkalov2018, Paulavicius2014, Sergeyev2015, Strongin2018, Gergel2017_2, Gergel2019}.

>>>>

\section{Numerical experiments}
\begin{figure}[h!]
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=\linewidth]{Simple_59_IA} \\ a)}
	\end{minipage}
	\hfill
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=\linewidth]{Simple_59_IA-DL} \\ b)}
	\end{minipage}
	\caption{Solving a Simple problem by IA (a) and IA-DL (b) methods}
	\label{fig:examples_simple}
\end{figure}

\begin{figure}[h!]
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=\linewidth]{Hard_7_IA} \\ a)}
	\end{minipage}
	\hfill
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=\linewidth]{Hard_7_IA-DL} \\ b)}
	\end{minipage}
	\caption{Solving a Hard problem by IA (a) and IA-DL (b) methods}
	\label{fig:examples_simple}
\end{figure}

\begin{table}[h!]
	\centering
		\begin{tabular}{ccccccccccccc}
			\hline
			& \multicolumn{2}{c}{$N=2$} & & \multicolumn{2}{c}{$N=3$} & & \multicolumn{2}{c}{$N=4$} & & \multicolumn{2}{c}{$N=5$} \\
			\cline{2-3} \cline{5-6} \cline{8-9} \cline{11-12}
			& \textit{Simple} & \textit{Hard} & & \textit{Simple} & \textit{Hard} & & \textit{Simple} & \textit{Hard} & & \textit{Simple} & \textit{Hard} \\
			\hline
			IA-DL, $r_{\nu}^{loc}=1.4$ & 316 & 766 & & 7403 & 9636 & & 44304 & 60904 & & 296357 & 763711 \\
			\hline
			IA-DL, $r_{\nu}^{loc}=2.0$ & 350 & 830 & & 8990(1) & 12020 & & 47133 & 57473 & & 360497 & 743874(1) \\
			\hline
			IA & 439 & 1074 & & 11804(1) & 20327 & & 42837 & 87310(2) & & 404660(2) & 1084990(2) \\
			\hline
		\end{tabular}
	\caption{Average number of iterations}
	\label{tab:average_number_of_iterations}
\end{table}

\begin{table}[h!]
	\centering
		\begin{tabular}{ccccc}
			\hline
			& $N=2$ & $N=3$ & $N=4$ & $N=5$ \\
			\hline
			IA-DL, $r_{\nu}^{loc}=1.4$ & 316 & 7403 & 44304 & 296357 \\
			\hline
			IA-DL, $r_{\nu}^{loc}=2.0$ & 350 & 8990(1) & 47133 & 360497 \\
			\hline
			IA & 439 & 11804(1) & 42837 & 404660(2) \\
			\hline
		\end{tabular}
	\caption{Average number of iterations Simple}
	\label{tab:average_number_of_iterations_simple}
\end{table}

\begin{table}[h!]
	\centering
		\begin{tabular}{ccccc}
			\hline
			& $N=2$ & $N=3$ & $N=4$ & $N=5$ \\
			\hline
			IA-DL, $r_{\nu}^{loc}=1.4$ & 766 & 9636 & 60904 & 763711 \\
			\hline
			IA-DL, $r_{\nu}^{loc}=2.0$ & 830 & 12020 & 57473 & 743874(1) \\
			\hline
			IA & 1074 & 20327 & 87310(2) & 1084990(2) \\
			\hline
		\end{tabular}
	\caption{Average number of iterations Hard}
	\label{tab:average_number_of_iterations_hard}
\end{table}

\begin{figure}[h!]
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=\linewidth]{Operating_characteristic_gklssC_3} \\ a)}
	\end{minipage}
	\hfill
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=\linewidth]{Operating_characteristic_gklshC_3} \\ b)}
	\end{minipage}
	\caption{Operational characteristics for Simple (a) and Hard (b) problems, $N=3$}
	\label{fig:operational_characteristics_N=3}
\end{figure}

\begin{figure}[h!]
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=\linewidth]{Operating_characteristic_gklssC_5} \\ a)}
	\end{minipage}
	\hfill
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=\linewidth]{Operating_characteristic_gklshC_5} \\ b)}
	\end{minipage}
	\caption{Operational characteristics for Simple (a) and Hard (b) problems, $N=5$}
	\label{fig:operational_characteristics_N=5}
\end{figure}

\begin{figure}[h!]
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=\linewidth]{Decision_rule_gklssC_4} \\ a)}
	\end{minipage}
	\hfill
	\begin{minipage}[h]{0.48\linewidth}
		\center{\includegraphics[width=\linewidth]{Decision_rule_gklshC_4} \\ b)}
	\end{minipage}
	\caption{Frequency of using various estimates of the Lipschitz constant for Simple (a) and Hard (b) problems, $N=4$}
	\label{fig:frequency_N=4}
\end{figure}

@@

\section{TEST}
\cite{Evtushenko1971, Piyavskii1972, Shubert1972, Strongin1970, Evtushenko2009, Evtushenko2013, Strongin2000, Sergeyev2013, Pinter1996, Jones2009, Wood1991, Meewella1988, Mladineo1986, Vaz2009, Stripinis2019, Paulavicius2016, Pillo2012, Pillo2016, Barkalov2017_1, Barkalov2017_2, Sergeyev2006, Zilinskas2008, Sovrasov2019, Kvasov2003, Sergeyev2010,Sergeyev2016, Horst1996, Gablonsky2001, Jones1993, Gaviano2003, Barkalov2018, Paulavicius2014, Sergeyev2015, Strongin2018, Gergel2017_2, Gergel2019}.
